Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-06-27 pirouette_article.tex
Start processing feedback @rsetienne
Moved section on stochasticity to supplementary materials, 3270 words

The goal of \verb;pirouette; is to quantify the \new{impact of a new} tree prior.
It does so by measuring the inference error made 
for a given reconstructed phylogeny, 
simulated under a (usually novel) diversification model.
We refer to the model that has generated the given tree 
as the 'generative tree model' $\mathit{p_{G}}$.
\rampal{
	This only increases the confusion; maybe replace by baseline model everywhere
}
\richel{
	I feel the new wording below is good enough. Replacing 'generative'
	by 'baseline' add to confusion when the generative model is the
	generative model. Giovanni, what do you think?
}
\new{
  A 'generative tree model', in this paper, is always a standard tree model.
  If the actual model that generated the tree is non-standard, 
  the 'generative tree model' is the standard tree model that is 
  closest to the actual model. In that case, the
  'generative tree model' serves as a baseline or comparison model.
}

@@

Similar to lab experiments, \verb;pirouette; allows to perform
two types of control measurements. The first type of control
is called 'twinning', which results in an error distribution
that is the baseline error of the inference pipeline (see
supplementary materials, section \ref{subsec:twinning} for more details).
The second type of control is the use of candidate models,
which results in an error distribution
for a generative model that is determined to be the best fit to
the tree (see supplementary materials, 
section \ref{subsec:candidates} for more details).

\subsection{Stochasticity caused by simulating phylogenies}

Finally, if the goal is to evaluate BEAST2's performance 
on a non-standard tree model, 
one must also consider the last source of stochasticity: 
the different phylogenies a tree model generates.
A single phylogeny cannot be considered as fully representative of the model. 
For this reason multiple phylogenies must be 
considered \new{(at least 100 independent true and twin trees)}.
If the number of considered phylogenies is high enough, 
the comparison between the main pipeline's aggregated error distribution 
and its twin counterpart leads to a fair evaluation 
of the new tree model with respect to the baseline error.

>>>>

The goal of \verb;pirouette; is to quantify the \new{impact of a new} tree prior.
It does so by measuring the inference error made 
for a given reconstructed phylogeny, 
simulated under a (usually novel) diversification model.
We refer to the model that has generated the given tree 
as the 'generative tree model' $\mathit{p_{G}}$.
\rampal{
	Perhaps if you replace by "generative model for the twin tree", 
	then it is fine.
}
\new{
  A 'generative tree model', in this paper, is always a standard tree model.
  If the actual model that generated the tree is non-standard, 
  the 'generative tree model' is the standard tree model that is 
  closest to the actual model. In that case, the
  'generative tree model' serves as a baseline model.
  This is is done in the example, where the Yule model is the generative model.
}

@@

Similar to lab experiments, \verb;pirouette; allows to perform
two types of control measurements. The first type of control
is called 'twinning', which results in an error distribution
that is the baseline error of the inference pipeline (see
supplementary materials, section \ref{subsec:twinning} for more details).
The second type of control is the use of candidate models,
which results in an error distribution
for a generative model that is determined to be the best fit to
the tree (see supplementary materials, 
section \ref{subsec:candidates} for more details).
Additionally, multiple \verb;pirouette; runs are needed
to reduce the influence of stochasticity (see supplementary materials, 
section \ref{subsec:stochasticity} for more details).

### 2020-06-27 pirouette_supplement.tex
Moved section on stochasticity to supplementary materials, 3270 words

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stochasticity caused by simulating phylogenies}
\label{subsec:stochasticity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The goal is to evaluate BEAST2's performance 
on a non-standard tree model, 
one must also consider the last source of stochasticity: 
the different phylogenies a tree model generates.
A single phylogeny cannot be considered as fully representative of the model. 
For this reason multiple phylogenies must be 
considered \new{(at least 100 independent true and twin trees)}.
If the number of considered phylogenies is high enough, 
the comparison between the main pipeline's aggregated error distribution 
and its twin counterpart leads to a fair evaluation 
of the new tree model with respect to the baseline error.
